Evaluating KNN, SVR, ANN, XGBoost Regressor, Linear Regression, and Random Forest Models for Dengue Case Prediction: A Comparative Study

### 2024-12-09 paper/main.tex
Modified format style

\documentclass{article}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{apacite}

@@

\title{\textbf{Evaluating KNN, SVR, ANN, XGBoost Regressor, Linear Regression, and Random Forest Models for Dengue Case Prediction: A Comparative Study}}
\author{
    Kurt Matthew Amodia \and 
    Glen Andrew Bulaong \and 
    Carl Benedict Elipan \and 
    John Hamir Karim
}
\date{}

\begin{document}
\maketitle

@@

Specifically, this study aims to:
\begin{enumerate}
    \item Gather dengue data from the Iloilo Provincial Health Office and climate data from online sources. Combine these data into a unified dataset to facilitate comprehensive dengue case forecasting.
    \item Train and evaluate model metrics, including K-Nearest Neighbors (KNN), Linear Regression, Support Vector Regressor (SVR), Random Forest, Artificial Neural Network (ANN), and XGBoost Regressor for predicting dengue cases.
    \item Compare the performance of these models to determine the most accurate forecasting approach.
\end{enumerate}

@@

\subsubsection{Data Integration and Preprocessing}
The dengue case data was integrated with the weather data to create a comprehensive dataset, aligning the data based on corresponding timeframes. The dataset undergoed a cleaning process to address any missing values, outliers, and inconsistencies to ensure its accuracy and reliability. To ensure that all features and the target variable were on the same scale, a MinMaxScaler was applied to normalize both the input features (rainfall, temperature, humidity) and the target variable (dengue cases). To enhance the quality of the data and minimize the impact of random short-term fluctuations, moving averages was applied to selected columns, including rainfall, humidity, and temperature. This approach will help to filter out 'noise' and provide a clearer representation of the underlying trends.

>>>>

\documentclass[runningheads]{llncs}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{apacite}

@@

\begin{document}
\title{Evaluating KNN, SVR, ANN, XGBoost Regressor, Linear Regression, and Random Forest Models for Dengue Case Prediction: A Comparative Study}
%
%\titlerunning{Abbreviated paper title}
% If the paper title is too long for the running head, you can set
% an abbreviated paper title here
%
\author{Kurt Matthew Amodia, Glen Andrew Bulaong, Carl Benedict Elipan, John Hamir Karim, and Ara Abigail Ambita}
%
\authorrunning{K. Amodia et al.}
\titlerunning{Evaluating ML Models for Dengue Case Prediction}

\institute{Division of Physical Sciences and Mathematics\\
	University of the Philippines Visayas\\
	Miagao, Iloilo, Philippines\\
\email{\{kaamodia, gcbulaong, clelipan, jckarim\}@up.edu.ph}}
\maketitle

@@

Specifically, this study\footnote{Github Repository: \url{https://github.com/HENERALPEPITO/ML-miniproject.git}} aims to:
\begin{enumerate}
    \item Gather dengue data from the Iloilo Provincial Health Office and climate data from online sources. Combine these data into a unified dataset to facilitate comprehensive dengue case forecasting.
    \item Train and evaluate model metrics, including K-Nearest Neighbors (KNN), Linear Regression, Support Vector Regressor (SVR), Random Forest, Artificial Neural Network (ANN), and XGBoost Regressor for predicting dengue cases.
    \item Compare the performance of these models to determine the most accurate forecasting approach.
\end{enumerate}

@@

\subsubsection{Data Integration and Preprocessing}
The dengue case data was integrated with the weather data to create a comprehensive dataset\footnote{For reference of the complete dataset:\\ 
	\url{https://github.com/HENERALPEPITO/ML-miniproject/tree/main/datasets}}, aligning the data based on corresponding timeframes. The dataset undergoed a cleaning process to address any missing values, outliers, and inconsistencies to ensure its accuracy and reliability. To ensure that all features and the target variable were on the same scale, a MinMaxScaler was applied to normalize both the input features (rainfall, temperature, humidity) and the target variable (dengue cases). To enhance the quality of the data and minimize the impact of random short-term fluctuations, moving averages was applied to selected columns, including rainfall, humidity, and temperature. This approach will help to filter out 'noise' and provide a clearer representation of the underlying trends.
